Conservation of interaction partners between related plants varies widely across communities and between plant families.

### 2019-02-22 manuscript/phylogenetic_signal_manuscript.tex
arg, need details from the other copy

  We modelled the relationship between nich

e overlap and phylogenetic distance
  using a logistic regression. We used both the numbers of shared ($M_{ij}$)and 
  non-shared ($U_{ij}$) partners as dependent variables and centred, scaled phylogenetic 
  distance as the independent variable. This approach is conceptually similar to 
  modelling successes and failures in a binomial-distributed process. 
  Accordingly, we assumed a binomial distribution for residuals. Regressions of
  niche overlap and phylogenetic distance within each network were fit using the
  R~\citep{R} base function ``glm''. These separate regressions avoid the potential
  for confounding the effects of different relationships in different networks. As
  we also wished to evaluate the overall trend across networks, we fit an additional
  regression of niche overlap and phylogenetic distance across all network types.
  As well as the fixed effect of phylogenetic distance, this regression included 
  fixed effects of network type (pollination or herbivory) and the interaction 
  between phylogenetic network type and random intercepts and slopes per network.
  This expanded regression was fit using the R~\citep{R} function ``glmer'' from
  package \emph{lme4}~\citep{lme4}.

@@

  This permutation approach also allows us to estimate type I and type II 
  error for our analysis. To do this, we created 500 permutations of each 
  permuted network and, again keeping the observed phylogenetic distances 
  between plant species, repeated our analyses. We can then determine the 
  number of permuted networks which appear to have significant 
  overlap-phylogenetic distance relationships relative to the permutations 
  of these permuted networks (type I error). Type II error can be determined
  from the distribution of p-values obtained when comparing the permuted 
  networks to permutations of the permuted networks. The distribution of 
  p-values should be uniform. [[I still do not see how this gives us the
  probability of a false negative... ]] [[Something to do with comparing
  the distributions of p-values from glmer and the ones from the randomization.
  I don't think I actually kept the p-values from glmer, but the p-values from
  the randomizations are bang-on uniform.]]
  [[Maybe go back to whichever reviewer comment this was based on?]]
  [[How does this get at type II error?]] 
  [[Seems we can calculate power for a specific alternative hypothesis by
  comparing distributions of p-values from glmer and from the permutations.
  I can only pray I kept the p-values from the randomised regressions...]]

@@

  [[I need to double-check that I'm actually doing this, and that the right things
  are being plotted.]][[I think I may not have updated this since the family composition 
  was not singificant. Still of interest, so redo. Guess I will also need to do randomisations
  to make the p-vals here?]]

@@

  For each plant family, within each network type, we then fit one of two similar 
  sets of models. First, when family $f$ was found in several networks of network
  type $t$, we fit mixed-effects logistic regressions for the probability of sharing an interaction partner $\omega_{ntfij}$ of the form
  \begin{equation}
    logit(\omega_{ntfij}) \propto \delta_{ij} + N_{n} ,
    \label{full}
  \end{equation}

  \noindent where $\omega_{tnfij}$ is the probability of sharing a partner 
  in network $n$ of network type $t$ for plants $i$ and $j$ in plant family $f$,
  $\delta_{ij}$ is the phylogenetic distance between plants $i$ and $j$, and
  $N_{n}$ is a random effect of network $n$.
  Second, if a plant family was represented in only one network 
  and therefore necessarily in only one network type, we omitted the 
  network-level random effect giving mixed-effects logistic regressions of the form
 \begin{equation}
    logit(\omega_{pntfij}) \propto \delta_{ij} .
    \label{minimal}
  \end{equation}

  \noindent We fit Eq.~\ref{full} using the function `glmer' from the
  R package lme4~\citep{lme4} and fit Eq.~\ref{minimal} in R using the
  function `glm' from the same package.

@@

  \subsection*{Within-network conservation of niche overlap}

    Across all networks, overlap of interaction partners decreased with increasing phylogenetic distance and the decrease in overlap of pollinators was steeper than that in herbivores ($\beta_{distance}$=-6.82, $p$\textless0.001 and $\beta_{distance:PP}$=-18.5, $p$\textless0.001, respectively). That is, a pair of plants in the same genus was more likely to share interaction partners than a pair of plants in the same family in both types of networks, but a pair of congeners would be less likely to share pollinators than to share herbivores. Regardless of phylogenetic distance, a pair of plants were also less likely to share pollinators than herbivores ($\beta_{PP}$=-1.44, $p$\textless0.001). This may be due to the greater proportion of
    specialist pollinators than specialist herbivores. In our dataset, an
    average of 48\% (+/- 14) of pollinators in a given web were extreme 
    specialists (i.e., visited only one plant species) compared to 29\% 
    (+/- 29) of herbivores ($z$=5.62, df=68, $P$\textless0.001 
    for a binomial regression of specialists and generalists over network
    type). % Are the above betas un-scaled?

@@

    [[Reviewers demanded this - it seems very boring]]
    Comparing the results in the observed networks to those obtained after permuting phylogenetic distances across pairs of plants, the observed slope of the relationship between phylogenetic distance and interaction partner overlap was always more extreme (i.e., always lesser or always greater) than that obtained in the permuted networks (Fig.~\ref{obs_vs_random}). Observed networks with a negative relationship between phylogenetic distance and overlap always had a more negative slope than that obtained from the permuted networks, while the 10 networks with positive relationships between phylogenetic distance and overlap always had more positive relationships than the permuted networks.

@@

  \subsection*{Within-family conservation of niche overlap} [[Still of interest given negative result above?]]

>>>>

  We modelled the relationship between niche overlap and phylogenetic distance
  using a logistic regression. We used both the numbers of shared ($M_{ij}$)and 
  non-shared ($U_{ij}$) partners as dependent variables and centred, scaled phylogenetic 
  distance as the independent variable. This approach is conceptually similar to 
  modelling successes and failures in a binomial-distributed process. 
  Accordingly, we assumed a binomial distribution for residuals. Regressions of
  niche overlap and phylogenetic distance within each network were fit using the
  R~\citep{R} base function ``glm'' and took the form. The fixed effect of distance
  in this regression, $\beta_{distance}$, can
  be understood as the change in log odds of sharing an interaction partner per
  million-year change in phylogenetic distance.

  These separate regressions avoid the potential
  for confounding the effects of different relationships in different networks. As
  we also wished to evaluate the overall trend across networks, we fit an additional
  regression of niche overlap and phylogenetic distance across all network types.
  As well as the fixed effect of phylogenetic distance, this regression included 
  fixed effects of network type (pollination or herbivory) and the interaction 
  between phylogenetic network type and random intercepts and slopes per network.
  This expanded regression was fit using the R~\citep{R} function ``glmer'' from
  package \emph{lme4}~\citep{lme4}.

@@

  This permutation approach also allows us to estimate type I and type II 
  error for our analysis. To do this, we created 500 permutations of each 
  permuted network and, again keeping the observed phylogenetic distances 
  between plant species, repeated our analyses. We can then determine the 
  number of permuted networks which appear to have significant 
  overlap-phylogenetic distance relationships relative to the permutations 
  of these permuted networks (type I error). Type II error can be determined
  from the distribution of p-values obtained when comparing the permuted 
  networks to permutations of the permuted networks. Although calculating the
  exact type II error requires a specific alternative hypothesis, the uniform
  distribution of p-values we obtained after permuting the permuted networks
  means that the type II error would increase linearly as the alternative 
  hypothesis was set farther from zero. [[Is this cogent? Correct? If not, I think I
  will have to remove all reference to type II error and hope we don't get the
  same reviewer again. It may not be an issue since we've moved away from the
  motif-like measures.]]

@@

@@

  For each plant family, within each network type, we then fit one of two similar 
  sets of models. If family $f$ was found in several networks of the same type
  (e.g., several pollination networks), we fit a mixed-effects logistic regression
  relating niche overlap to a fixed effect of phylogenetic distance and a random
  effect for each network using the R~\citep{R} function ``glmer'' from
  package \emph{lme4}~\citep{lme4}. If family $f$ was found in only one network
  (and therefore only one network type), we omitted the 
  network-level random effect and fit a logistic regression using the R~\citep{R}
  base function ``glm''. [[We didn't use equations to explain the first round
  of logistic regressions, so not sure why I was doing that here...]]

@@

  \subsection*{Within-network conservation of niche overlap} [[ok, need to make some updates here.]]

    Across all networks, overlap of interaction partners decreased with increasing phylogenetic distance and the decrease in overlap of pollinators was steeper than that in herbivores ($\beta_{distance:herbivory}$=-6.82, $p$\textless0.001 and $\beta_{distance:pollination}$=-18.5, $p$\textless0.001, respectively). That is, a pair of plants in the same genus was more likely to share interaction partners than a pair of plants in the same family in both types of networks, but a pair of congeners would be less likely to share pollinators than to share herbivores. Regardless of phylogenetic distance, a pair of plants were also less likely to share pollinators than herbivores ($\beta_{PP}$=-1.44, $p$\textless0.001). This may be due to the greater proportion of
    specialist pollinators than specialist herbivores. In our dataset, an
    average of 48\% (+/- 14) of pollinators in a given web were extreme 
    specialists (i.e., visited only one plant species) compared to 29\% 
    (+/- 29) of herbivores ($z$=5.62, df=68, $P$\textless0.001 
    for a binomial regression of specialists and generalists over network
    type). % Are the above betas un-scaled?

@@

    [[Reviewers demanded this - it seems very boring]]
    Comparing the results in the observed networks to those obtained after permuting phylogenetic distances across pairs of plants, the observed slope of the relationship between phylogenetic distance and interaction partner overlap was always more extreme (i.e., always lesser or always greater) than that obtained in the permuted networks (Fig.~\ref{obs_vs_random}). Observed networks with a negative relationship between phylogenetic distance and overlap always had a more negative slope than that obtained from the permuted networks, while the 10 networks with positive relationships between phylogenetic distance and overlap always had more positive relationships than the permuted networks. This suggests that even in the networks with non-significant relationships between niche overlap and phylogenetic distance, the association between niche overlap and phylogenetic distance was not random.

@@

  \subsection*{Within-family conservation of niche overlap}
